%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[TBL around wing sections] % Short title used in healines (optional)
{%
 High-fidelity simulations of the flow around wings at high Reynolds numbers% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{High-fidelity simulations of the flow around wings at high Reynolds numbers} % Title for toc
%
\paperauthor[Vinuesa \etal] % Short authors used in headlines and List Of Papers
{%
  R. Vinuesa, P. S. Negi, A. Hanifi, D. S. Henningson and P. Schlatter%
}%
%
\listpaperauthor{Vinuesa, Negi, Hanifi, Henningson \& Schlatter}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
%  $^1$ Linn\'e FLOW Centre, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
%  $^2$ Super-laser LAB, The Death Star, not orbiting Alderaan anymore ;)%
%  Linn\'e FLOW Centre, KTH Mechanics, S-100 44 Stockholm, Sweden\\
%  Swedish e-Science Research Centre (SeRC), SE-100 44, Stockholm, Sweden%
Department of Mechanics, Linn\'e FLOW Centre and Swedish e-Science Research Centre (SeRC), KTH Royal Institute of Technology, SE-100 44 Stockholm, Sweden 
}%
%
\paperjournal[Proc. TSFP-10] % Short publish info used in List Of Papers
{%
	In Proc. $10^{th}$ Int. Sym. on Turbulence \& Shear Flow Phenomenon (TSFP-10)
}%
%
\papervolume{}%
%
%\papernumber{1}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction) 
	Reynolds-number effects in the adverse-pressure-gradient (APG) turbulent boundary layer (TBL) developing on the suction side of a NACA4412 wing section are assessed in the present work. To this end, we conducted a well-resolved large-eddy simulation of the turbulent flow around the NACA4412 airfoil at a Reynolds number based on freestream velocity and chord length of $Re_{c}=1,000,000$, with $5^{\circ}$ angle of attack. The results of this simulation are used, together with the direct numerical simulation by Hosseini {\it et al.} (Int. J. Heat Fluid Flow {\bf 61}, 2016) of the same wing section at $Re_{c}=400,000$, to characterize the effect of Reynolds number on APG TBLs subjected to the same pressure-gradient distribution (defined by the Caluser pressure-gradient parameter $\beta$). Our results indicate that the increase in inner-scaled edge velocity $U^{+}_{e}$, and the decrease in shape factor $H$, is lower in the APG on the wing than in zero-pressure-gradient (ZPG) TBLs over the same Reynolds-number range. This indicates that the lower-$Re$ boundary layer is more sensitive to the effect of the APG, a conclusion that is supported by the larger values in the outer region of the tangential velocity fluctuation profile in the $Re_{c}=400,000$ wing. Future extensions of the present work will be aimed at studying the differences in the outer-region energizing mechanisms due to APGs and increasing Reynolds number.
}%
%
\graphicspath{{paper4/imgs/}{paper4/imgs2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

\makepapertitle

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
	Reynolds-number effects in the adverse-pressure-gradient (APG) turbulent boundary layer (TBL) developing on the suction side of a NACA4412 wing section are assessed in the present work. To this end, we conducted a well-resolved large-eddy simulation of the turbulent flow around the NACA4412 airfoil at a Reynolds number based on freestream velocity and chord length of $Re_{c}=1,000,000$, with $5^{\circ}$ angle of attack. The results of this simulation are used, together with the direct numerical simulation by Hosseini {\it et al.} (Int. J. Heat Fluid Flow {\bf 61}, 2016) of the same wing section at $Re_{c}=400,000$, to characterize the effect of Reynolds number on APG TBLs subjected to the same pressure-gradient distribution (defined by the Caluser pressure-gradient parameter $\beta$). Our results indicate that the increase in inner-scaled edge velocity $U^{+}_{e}$, and the decrease in shape factor $H$, is lower in the APG on the wing than in zero-pressure-gradient (ZPG) TBLs over the same Reynolds-number range. This indicates that the lower-$Re$ boundary layer is more sensitive to the effect of the APG, a conclusion that is supported by the larger values in the outer region of the tangential velocity fluctuation profile in the $Re_{c}=400,000$ wing. Future extensions of the present work will be aimed at studying the differences in the outer-region energizing mechanisms due to APGs and increasing Reynolds number.
    \keywords{adverse pressure-gradient, boundary-layer, wings}
\end{paperabstract}


%------------------------------------------------------------------------------
% Article
%------------------------------------------------------------------------------
%
\input{paper4/article2.tex}


%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
%\clearpage
\bibliographystyle{jfm}
\bibliography{licentiate}
%
\IfFileExists{paper4/paper.bbl}{\input{paper4/paper.bbl}}{}
\pagebreak

\appendix

\section{Domain Validation}
\label{appendix:domain_validation}
\input{paper4/appendix.tex}


%===============================================================================
%                            END PAPER
%===============================================================================
\end{paper}
