

\begin{acknowledgements}
	My foremost gratitude goes to my supervisor Dan Henningson for giving me the opportunity to join his research group. His knowledge and guidance have helped me immensely as a student. His encouragement, for which there is no substitute, have always provided the inspiration I needed to constantly push myself further in my work. Next I would like to thank my co-advisors Philipp Schlatter and Ardeshir Hanifi. Philipp for his patience during all my ignorant and sometimes foolish questions on numerics, conferences, papers and others that I probably can't recall. Ardeshir for the laughter, the sandwiches, the beers and most importantly, always being available on short notice when I needed help. I would also like to thank the members of the NFFP project, Roger Larsson, Dr. David Eller and Dr. Mikaela Lokatt for all the interesting discussions on aerodynamics. 
	
	I am grateful to Adam Peplinski for all the help he provided with Nek5000, MPI and coding in general. I can not imagine figuring out the workings of Nek5000 without his support. Armin and Ricardo have helped me more than others during my crucial time as a new Phd student. The help is greatly appreciated.
	
	Special mentions go to Mattias for all the coffee breaks, introducing me to Swedish food, the spontaneous discussions and being the bouncing board for all my (mostly wrong) ideas. Your company shall be missed once you leave the department. Jacopo and Giandomenico for all the great company, joining for the spontaneous plans and granting me the honorary Italian citizenship. I'll learn Italian very soon I promise! Marco for the constant dinner company. Freddy for the weekend food+beer+movie routine. Elektra for being one of the greatest friends of all time. Politics, late-night and of course Trump shall keep us entertained for times to come. But mostly, thanks for correcting my manuscripts and the support during this licentiate period. A mention must also go to my unrequited love, Walter Fornari. Where will I find another like you?
	
	A hearty thanks goes out to all my friends here at the department who make this a wonderful place. Eric, Clio, Nicolas, Sudhakar, Ugis, Evelyn, Anthony, Mehdi, Ali, Guillaume, Luca, Luca, Pierluigi, enrico, Francesco, Kristina, Ekatrina, J.C., Matthias, Priti, Ninge, Sagar, Krishne, Dhiya, and everyone else. All of you, with your quirks, jokes, stories and gossip (looking at you Pierluigi) add a little bit of color to life everyday.
	
	Perhaps most importantly, my deepest gratitude goes towards my family for their patience, unconditional love and support during my ever wandering path through life.
	
	Lastly, financial support for this work was provided by Vinnova through the NFFP project UMTAPS, with grant number 2014-00933, the Knut and Alice Wallenberg Foundation, and the European Research Council under grant agreement 694452-TRANSEP-ERC-2015-AdG.\ The computations were performed on resources provided by the Swedish National Infrastructure for Computing (SNIC) at the PDC Center for High Performance Computing at the Royal Institute of Technology (KTH). Simulation have also been performed at the Barcelona Supercomputing Center, Barcelona, with computer time provided by the $12^{th}$ PRACE Project Access Call (number 2015133182) and at the High Performance Computing Center, Stuttgart (HLRS) with the computer time provided by the $15^{th}$ PRACE Project Access Call (number 2016163965). 

\end{acknowledgements}
