%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Rexalation-term stabilization] % Short title used in headlines (optional)
{%
  A re-examination of filter-based stabilization for spectral element methods% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Relaxation-term-based stabilization} % Title for toc
%
\paperauthor[Negi P. S.] % Short authors used in headlines and List Of Papers
{%
  P. S. Negi %$^{1,2}$, P. Schlatter$^{1,2}$, A. Hanifi$^{1}$ and D. S. Henningson$^{1,2}$%
}%
%
%\listpaperauthor{A. Skywalker \& D. Vader}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
%  $^1$ Linn\'e FLOW Centre, KTH Mechanics, S-100 44 Stockholm, Sweden\\
%  $^2$ Swedish e-Science Research Centre (SeRC), SE-100 44, Stockholm, Sweden%
  Linn\'e FLOW Centre, KTH Mechanics, S-100 44 Stockholm, Sweden\\
  Swedish e-Science Research Centre (SeRC), SE-100 44, Stockholm, Sweden%
}%
%
\paperjournal[Gal. Empire Publ.] % Short publish info used in List Of Papers
{%
	Galactic Empire Publications%
}%
%
\papervolume{42}%
%
\papernumber{2}%
%
\paperpages{1--10}%
%
\paperyear{3639}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction) 
	The implications of concurrent archetypes have been far-reaching and
	pervasive. Given the current status of heterogeneous technology,
	cyberinformaticians daringly desire the key unification of the Turing
	machine and erasure coding. We explore new decentralized information,
	which we call Tuna.
}%
%
\graphicspath{{stabilization/imgs/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

\makepapertitle

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
	We revisit the ``filter-based stabilization'' approach proposed by \cite{fischer01} and find that it suffers from several drawbacks. In particular the ``evolve and filter'' approach causes a violation of the divergence-free condition which can be particularly severe in the cases of marginally resolved flows. Moreover the form of the filtering operation causes the filter to not be purely dissipative. Instead of a filter-based approach we propose to use a ``relaxation-term-based stabilization'' which we refer to as an RT stabilization, which is very closely related to the explicit filtering operation. The method retains the advantages of simplicity and efficiency of a filter based approach while also remedying the above mentioned drawbacks. Parameter limits of such a stabilization procedure are explored and the method is shown to be effective within the practical parameter ranges.
\end{paperabstract}


%------------------------------------------------------------------------------
% Article
%------------------------------------------------------------------------------
%
\input{stabilization/article.tex}


%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
%\clearpage
\bibliographystyle{jfm}
\bibliography{licentiate}
%
%\IfFileExists{stabilization/paper.bbl}{\input{stabilization/paper.bbl}}{}

%===============================================================================
%                            END PAPER
%===============================================================================
\end{paper}
